```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Installation

```{r,eval = FALSE}
devtools::install_git("https://gitlab.com/lajh87/d3tm")
```

## Usage

```{r}
library(d3tm)
data.frame(Titanic) %>%
 dplyr::select(Class,Age,Survived,Sex,Freq) %>%
  d3_nest2(value_col="Freq", root="Titanic",
           id_vars = c("Class", "Age", "Sex", "Survived")) %>%
  ztm()

```

## Detail

Introduced by [Ben Shneiderman](http://www.cs.umd.edu/hcil/treemap-history/) 
in 1991, a treemap recursively subdivides area into rectangles according to each 
node’s associated value. 

The treemap above uses interaction to reveal the hierarchy incrementally: 
clicking on a node zooms in. Only two levels of the hierarchy are visible at a time. 
This allows the layout’s aspect ratio 
[(ideally φ)](https://en.wikipedia.org/wiki/Golden_ratio) 
to be optimized for the current view, rather than computing a global layout. 
It also allows the exploration of arbitrarily-large datasets: 
data can be lazily-loaded and positioned on zoom.
